\section{Dataset}\label{Sec:Dat}
\subsection{Description}
We have decided to chose our own dataset, namely a list with movies. 
We got the dataset from the OMDb api. 
The OMDb API is a free web service to obtain movie information.
Alll content and images on the site are contributed and maintained by their users.
They also have a monthly database dump.
To save time we have decided not to use the OMDb api, but instead use their monthly database dump.
The list contains 938.037 movies.
For each movie we have the following information:\\
\textbf{ID} \\
This attribute contains the ID of the movie. \\
\textbf{IMDb ID} \\
This attribute contains the IMDb ID of the movie. \\
\textbf{Title} \\
This attribute contains the title of the movie. \\
\textbf{Year} \\
This attribute contains the year the movie was produced. 
This year can be difference from the release date.
For example there was a movie produced in 1896, which was released in 2011 on a film festival. \\
 \textbf{Rating} \\
This attribute contains the rating of the movie. 
This rating is for example 18+ for adult movies. 
This is not a rating for how good or bad the movie was.\\
 \textbf{Runtime} \\
This attribute contains the runtime of the movie.\\
 \textbf{Genre} \\
This attribute contains all genres of the movie. Each movie can have multiple genres.\\
 \textbf{Released} \\
This attribute contains the release data of the movie. \\
 \textbf{Director} \\
This attribute contains the director of the movie.\\
 \textbf{Writer} \\
This attribute contains the writer of the movie. \\
 \textbf{Cast} \\
This attribute contains the actors of the movie.\\
 \textbf{Metacritic} \\
This attribute contains the metacritic rating for the movie. 
This rating is based on multiple reviews of the movie.\\
 \textbf{IMDbRating} \\
This attribute contains the IMDb rating for the movie.
This rating is based on user votes. \\
 \textbf{IMDbVotes} \\
This attribute contains the number of votes on the movie. \\
 \textbf{Poster} \\
This attribute contains a link to an image of the movie poster. \\
 \textbf{Plot} \\
This attribute contains the plot for the movie. \\
 \textbf{FullPlot} \\
This attribute contains the full plot for the movie. 
This is a longer version of the plot. \\
 \textbf{Language} \\
This attribute contains the language which is spoken in the movie. \\
 \textbf{Country} \\
This attribute contains the of the movie.
The country of the movie is where the producers of the movie are located. \\
 \textbf{Awards} \\
This attribute contains the number of rewards the movie has won. \\
 \textbf{lastUpdated} \\
This attribute contains when the last update was made to the information of tthat movie. \\




