\section{Tasks}\label{Sec:Tas}
\subsection{Data analysis}
Since our data set contains data of a lot of movies, we are not really interested in individual movies.
If we wanted to analysis individual movies, we would have taken a smaller data set.
The data set we use contains movies from a time span of more than one hundred years.
From 1900 there was a movie released at least once every month.
We think it is interesting to find out when what type of movies were popular or not.
There are multiple ways to find define the type of the movie. 
We have chosen to look at the most obvious way of defining the type of the movie: by looking at the genre of the movie.
The genres of movies did not change over time. 
This way we can find out when each genre where first developped or if they were always there. 
There are multiple ways to measure the popularity of movies. 
Maybe when those type of movies get higher ratings or when those movies are produced more than normal. 
\subsection{Trend analysis of genres over time }
There are several questions that could come up at this subject, but we will focus mainly on the following three questions:
\begin{itemize}
\item \textbf{How popular is this genre?}
We think it might be interesting to know when certain genres were popular and how popular they are. 
\item \textbf{Is this genre becoming more popular again?}
We think it might be interesting to know if a certain genre is becoming more popular again. 
This could be useful for film producers, so they can focus on more popular genres. 
\item \textbf{When did this genre become popular for the first time?} 
We think it could be interesting to find out what the origins of a genre are. 
If we know when it became popular, we can look for reasons why this genre did became more popular.
\end{itemize}
\subsection{Perceived quality of genres over time }
There are several questions that could come up at this subject, but we will focus mainly on the following three questions:
\begin{itemize}
\item \textbf{Does this genre gets better ratings than before? }
We think it might be interesting to know when certain genres were perceived better. 
\item \textbf{Did this genre got a higher average rating for a longer time?}
We think it could be interesting to find ups and downs in the rating. 
When you knew the ratings went up, you can analyse that part to find the reason for that.
\item \textbf{Is there a correlation between higher ratings and more produced movies?} 
We think it might be interesting to find a relationship between higher ratings and the number of produced movies.
\end{itemize}


